\specsection{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\begingroup
\renewcommand{\section}[2]{}
\begin{thebibliography}{}
	
\bibitem{future_dir}
Benetos E., Dixon S., Giannoulis D., Kirchhoff H., Klapuri A. Automatic music transcription: challenges and future directions // Journal of Intelligent Information Systems. - 2013. - С. 407-434.

\bibitem{grouv}
Музыкальный словарь Гроува. М., 2007, С. 858.

\bibitem{chehovich}
Чехович Д. О. Ритм музыкальный // Большая российская энциклопедия. Том 28. Москва, 2015, С. 541.

\bibitem{quantize}
Cemgil A.T., Desain P., Kappen B. Rhythm quantization for transcription // Computer Music Journal. - 2000. - С. 60-76.

\bibitem{polikar}
Polikar R. The wavelet tutorial. - 2-е изд. - 2001. - 67 с.

\bibitem{dwt}
Tzanetakis G., Essl G., Cook P. Audio analysis using the Discrete Wavelet Transform // 2001.

\bibitem{samples}
Биккенин Р. Р., Чесноков М. Н. Теория электрической связи. - 2010. - 329 с.

\bibitem{midi}
Pleshkova S., Panchev K., Bekyarski A. Development of a MIDI synthesizer for test signals to a wireless acoustic sensor network // 2020.

\bibitem{hmm}
Takeda H., Saito N., Otsuki T. Hidden Markov model for automatic transcription of MIDI signals // 2002. - С. 428-431.

\bibitem{bayesian}
Nakamura E., Itoyama K., Yoshii K. Rhythm transcription of MIDI performances based on Hierarchical Bayesian Modelling of repetition and modification of musical note patterns // 2016.

\bibitem{syncope}
Hoffman M. Syncopation. - 2009.

\bibitem{dirichlet}
Kotz S., Balakrishnan N., Johnson N.L. Continuous Multivariate Distributions. Volume 1: Models and Applications (Chapter 49: Dirichlet and Inverted Dirichlet Distributions). - New York: Wiley, 2000.

\bibitem{mels}
Stevens S.S., Volkmann J., Newman E.B. A scale for the measurement of the psychological magnitude pitch // Acoustical Society of America. - 1937. - С. 188.

\bibitem{cnn}
Schreiber H., Muller M. A single-step approach to musical tempo estimation using a convolutional neural network // 2018. - С. 98-105.

\bibitem{elu}
Clevert D.A., Unterthiner T., Hochreiter S. Fast and accurate deep network learning by exponential linear units (elus) // 2015.

\bibitem{batch}
Ioffe S., Szegedy C. Batch normalization: Accelerating deep network training by reducing internal covariate shift // 2015.

\end{thebibliography}
\endgroup