\specsection{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\begingroup
\renewcommand{\section}[2]{}
\begin{thebibliography}{}
	
\bibitem{future_dir}
Benetos E. Automatic music transcription: challenges and future directions / Benetos E., Dixon S., Giannoulis D., Kirchhoff H., Klapuri A. // Journal of Intelligent Information Systems. -- 2013. -- С. 407-434.

\bibitem{grouv}
Музыкальный словарь Гроува. // Москва. -- 2007. -- С. 858.

\bibitem{chehovich}
Чехович Д. О. Ритм музыкальный // Большая российская энциклопедия. Москва. -- 2015. -- Том 28. -- С. 541.

\bibitem{rhythm}
Sachs C. Rhythm and tempo: a study in music history. -- 1953.

\bibitem{quantize}
Cemgil A. T., Desain P., Kappen B. Rhythm quantization for transcription // Computer Music Journal. -- 2000. -- С. 60-76.

\bibitem{polikar}
Polikar R. The wavelet tutorial // 2-е изд. -- 2001. -- 67 с.

\bibitem{dwt}
Tzanetakis G., Essl G., Cook P. Audio analysis using the Discrete Wavelet Transform. -- 2001.

\bibitem{samples}
Биккенин Р. Р., Чесноков М. Н. Теория электрической связи. -- 2010. -- 329 с.

\bibitem{midi}
Pleshkova S., Panchev K., Bekyarski A. Development of a MIDI synthesizer for test signals to a wireless acoustic sensor network. -- 2020.

\bibitem{hmm}
Takeda H., Saito N., Otsuki T. Hidden Markov model for automatic transcription of MIDI signals. -- 2002. -- С. 428-431.

\bibitem{kubler_pymc3}
Kübler R. Bayesian Hierarchical Modeling in PyMC3. -- 2021.

\bibitem{bayes_hier}
Rouder J. N., Lu J. An introduction to Bayesian hierarchical models with an application in the theory of signal detection // Psychonomic Bulletin \& Review. -- 2005. -- С. 573-604.

\bibitem{bayesian}
Nakamura E., Itoyama K., Yoshii K. Rhythm transcription of MIDI performances based on Hierarchical Bayesian Modelling of repetition and modification of musical note patterns. -- 2016.

\bibitem{mels}
Stevens S.S., Volkmann J., Newman E.B. A scale for the measurement of the psychological magnitude pitch // Acoustical Society of America. -- 1937. -- С. 188.

\bibitem{cnn}
Schreiber H., Muller M. A single-step approach to musical tempo estimation using a convolutional neural network // 2018. -- С. 98-105.

\bibitem{elu}
Clevert D.A., Unterthiner T., Hochreiter S. Fast and accurate deep network learning by exponential linear units (elus). -- 2015.

\bibitem{batch}
Ioffe S., Szegedy C. Batch normalization: Accelerating deep network training by reducing internal covariate shift. -- 2015.

\bibitem{dataset}
Spotify Tracks Dataset [Электронный ресурс]. -- Режим доступа: https://www.kaggle.com/datasets/maharshipandya/-spotify-tracks-dataset (дата обращения: 15.05.2023).

\bibitem{librosa}
Librosa: audio and music processing in Python [Электронный ресурс]. -- Режим доступа: \url{https://librosa.org/doc/latest/index.html} (дата обращения: 17.05.2023).

\bibitem{pymc3_docs}
PyMC3 Documentation [Электронный ресурс]. -- Режим доступа: \url{https://www.pymc.io/projects/docs/en/v3/} (дата обращения: 17.05.2023).

\bibitem{numpy}
NumPy documentation [Электронный ресурс]. -- Режим доступа: \url{https://numpy.org/doc/stable/} (дата обращения: 17.05.2023).

\end{thebibliography}
\endgroup